### 2005-11-11 doc/EFA/efa.tex
*** empty log message ***

-realize an automata for each variable.

>>>>

Given an extended finite automaton $A=\langle Q, \Sigma, \delta,
q_i, Q_m, X, G ,x_0, X_m \rangle$ with simple guard and action
functions, the steps are:\\
- Form a regular FA, $A'$, from $A$ by removing $G$, $X$, $X_m$,
$x_0$ and rename (associate with the corresponding state) all
enabled events $\sigma$ with $q\sigma$.\\
- Realize an automata $A_{x_k}$ for each variable $x_k$, with marked "states" $X_{m,k}$ and with as many events as elements in $G$ .\\
- Synchronize all automata.
